---
title: "Prediction Assignment"
author: "Khine Woo"
date: "June 10, 2017"
output: html_document
---


## Goal of project

The goal of your project is to predict the manner in which they did the exercise. This is the "classe" variable in the training set. You may use any of the other variables to predict with. You should create a report describing how you built your model, how you used cross validation, what you think the expected out of sample error is, and why you made the choices you did. You will also use your prediction model to predict 20 different test cases.

##About Data Set

Participants were asked to perform one set of 10 repetitions of the Unilateral Dumbbell Biceps Curl in five different fashions:exactly according to the specification (Class A), throwing the elbows to the front (Class B), lifting the dumbbell only halfway (Class C), lowering the dumbbell only halfway (Class D) and throwing the hips to the front (Class E). More about dataset http://groupware.les.inf.puc-rio.br/public/papers/2013.Velloso.QAR-WLE.pdf.

 
##Loading Data Set

Load testing dataset and training dataset.

```{r}
set.seed(1234)
pml_training<-read.csv("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv", na.strings=c("NA","#DIV/0!",""))
pml_testing<-read.csv("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv", na.strings=c("NA","#DIV/0!",""))
```

##Cleaning Dataset

Most prediction algorithms are not build to handle missing data. So, first remove the columns which contains NA.

```{r}
pml_training<-pml_training[,colSums(is.na(pml_training))==0]
pml_testing<-pml_testing[,colSums(is.na(pml_testing))==0]
```

Some columns are not require to predict. So I remove unnessary columns.

```{r}
pml_testing<-pml_testing[,-c(1:7)]
pml_training<-pml_training[,-c(1:7)]
```

##Select Sample Data
Due to computation limitation of my computer, I only select 3000 rows of dataset.
```{r}
training<-pml_training[sample(nrow(pml_training), 3000), ]
```

##Data Slicing on my sample dataset

I choose small dataset. So I slice the dataset into 80% training set and 20% test set.
```{r}
library(caret)
# create training set indexes with 75% of data
inTrain <- createDataPartition(y=training$classe,p=0.80, list=FALSE)
# subset training data to training
training <- training[inTrain,]
# subset training data (the rest) to test
testing <- training[-inTrain,]
```

##Choosing the Random Forest

Random Forest
Random forests are a way of averaging multiple deep decision trees, trained on different parts of the same training set, with the goal of overcoming over-fitting problem of individual decision tree.
It is one of the most used/accurate algorithms along with boosting.

```{r}
library(randomForest)
randomForestTrain <- randomForest(classe ~. , data=training)
confusionMatrix(testing$classe,predict(randomForestTrain,testing))
```
The accurancy is 1. So I think this method is good.

##Prediction on testing dataset.

```{r}
predict(randomForestTrain,pml_testing)
```

